They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-12 presentation.qmd
rm val from pres

cod_rounds <- qs::qread('cod_rounds.qs')
val_rounds <- qs::qread('valorant_rounds.qs')
```

@@

font <- 'Titillium Web'
extrafont::loadfonts(quiet = TRUE)
theme_set(theme_minimal())
theme_update(
  text = element_text(family = font),
  title = element_text(size = 14, color = 'white'),
  plot.title = element_text(face = 'bold', size = 20, color = 'white'),
  plot.title.position = 'plot',
  plot.subtitle = element_text(size = 14, color = '#f1f1f1'),
  axis.text = element_text(color = 'white', size = 14),
  axis.title = element_text(size = 14, color = 'white', face = 'bold', hjust = 0.99),
  axis.line = element_blank(),
  panel.grid.major = element_line(color = gray_points),
  panel.grid.minor = element_line(color = gray_points),
  panel.grid.minor.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  strip.text = element_text(color = 'white', size = 16, face = 'bold'),
  plot.margin = margin(10, 10, 10, 10),
  plot.background = element_rect(fill = blackish_background, color = blackish_background),
  plot.caption = element_text(size = 12, color = 'white', hjust = 1),
  plot.caption.position = 'plot',
  plot.tag = ggtext::element_markdown(size = 12, color = 'white', hjust = 0),
  plot.tag.position = c(0.01, 0.01),
  panel.background = element_rect(fill = blackish_background, color = blackish_background)
)
update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
update_geom_defaults('point', list(color = 'white'))
update_geom_defaults('segment', list(color = 'white'))

add_logo <- function(
    path,
    path_logo,
    idx_x,
    idx_y,
    logo_scale = 0.1,
    adjust_x = TRUE,
    adjust_y = TRUE,
    path_suffix = '_w_logo',
    delete = TRUE
) {

  plot <- magick::image_read(path)
  logo_raw <- magick::image_read(path_logo)

  plot_height <- magick::image_info(plot)$height
  plot_width <- magick::image_info(plot)$width

  logo <- magick::image_scale(logo_raw, as.character(round(plot_width * logo_scale)))

  info <- magick::image_info(logo)
  logo_width <- info$width
  logo_height <- info$height

  x_pos <- plot_width - idx_x * plot_width
  y_pos <- plot_height - idx_y * plot_height

  if (adjust_x) {
    x_pos <- x_pos - logo_width
  }

  if (adjust_y) {
    y_pos <- y_pos - logo_height
  }

  offset <- paste0('+', x_pos, '+', y_pos)

  img <- magick::image_composite(plot, logo, offset = offset)
  ext <- tools::file_ext(path)
  rgx_ext <- sprintf('[.]%s$', ext)

  res <- magick::image_write(
    img,
    gsub(rgx_ext, sprintf('%s.%s', path_suffix, ext), path)
  )

  if (!delete) {
    return(res)
  }
  unlink(path, recursive = TRUE, force = TRUE)
  res
}

```

## Game types

::: fragment
### Search and Destroy (SnD) in Call of Duty (COD)

-   2020-2022 Call of Duty League (CDL) matches (qualifiers and majors)
-   4v4
-   First to 6 round wins
-   Teams swap sides (offense and defense) after every round
:::

<br/>

::: fragment
### A Plant/Defuse in Valorant

-   2021 Valorant Champions Tour (VCT) matches (qualifiers and majors)
-   5v5
-   First to 13 round wins
-   One team plays offense in 12 consecutive rounds before swapping sides
-   Must win by 2 rounds
:::

## How does a team win a round of COD SnD / Valorant plant/defuse?

@@

## COD SnD data overview

@@

## Valorant data overview

```{r}
#| label: descriptive-val-snd-stats
#| eval: true
val_n_series <- val_rounds |> 
  distinct(series_id) |> 
  nrow() |> 
  scales::comma()

val_n_rounds <- val_rounds |> 
  distinct(series_id, round) |> 
  nrow() |> 
  scales::comma()

val_o_win_prop_const <- val_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)
val_o_win_pct <- scales::percent(val_o_win_prop_const, accuracy = 0.1)
```

::: fragment
-   Total series: **`r val_n_series`**
:::

::: fragment
-   Total rounds: **`r val_n_rounds`**
:::

::: fragment
-   Offensive win %: **`r val_o_win_pct`**
:::

## What are your chances of winning the next round ([COD SnD]{.cod})?

```{r}
#| label: cod-funcs

common_cod_labs <- function(...) {
  list(
    ...,
    labs(
      caption = 'CDL SnD Major and Weekly matches, 2020 - present'
    )
  )
}

@@

  path <- ggsave(
    plot = p,
    filename = file.path('plots', filename),
    width = width * dpi,
    height = height * dpi,
    units = units,
    dpi = dpi,
    ...
  )
  is_cod <- filename |> str_detect('cod_')
  game <- ifelse(is_cod, 'cod', 'val')
  logo_scale <- ifelse(is_cod, 0.15, 0.07)
  add_logo(
    path,
    path_logo = file.path('images', sprintf('%s.png', game)),
    delete = FALSE,
    path_suffix = '',
    logo_scale = logo_scale,
    idx_x = 0.99,
    idx_y = 0.01,
    adjust_x = FALSE
  )
}

@@

## What are your chances of winning the next round ([COD SnD]{.cod})?

@@

## What are your chances of winning the next round ([Valorant]{.valorant})?

```{r}
#| label: val-funcs
drop_25th_round <- function(df) {
  df |> 
    filter(
      !(pre_cumu_w == 12 & pre_cumu_l == 12)
    )
}

val_e_o_win_series_prop <- crossing(
  pre_cumu_w = 0:12,
  pre_cumu_l = 0:12
) |> 
  drop_25th_round() |> 
  mutate(
    n_remain_max = 25 - (pre_cumu_w + pre_cumu_l),
    n_remain_w = 13 - pre_cumu_w,
    ## can i account for offense in this by rotating?
    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
  )

## Joshua Broas, vlr.gg
common_val_labs <- function(...) {
  list(
    ...,
    labs(
      caption = '2021 VCT matches'
    )
  )
}

common_val_heatmap_layers <- function(...) {
  list(
    ...,
    guides(
      fill = 'none'
    ),
    scale_x_continuous(
      labels = 0:12,
      breaks = seq(0.5, 12.5, by = 1),
      expand = c(0, 0)
    ),
    scale_y_continuous(
      labels = 0:12,
      breaks = seq(0.5, 12.5, by = 1),
      expand = c(0, 0),
      sec.axis = sec_axis(
        trans = I, 
        name = ' ', 
        breaks = seq(0.5, 12.5, by = 1), 
        labels = rep('', 13)
      )
    ),
    theme(
      panel.grid.major = element_blank(),
      axis.title = element_text(hjust = 0.5),
      plot.title = ggtext::element_markdown(hjust = 0.5),
      axis.text = element_text(size = 16, face = 'bold')
    ),
    common_val_labs(),
    labs(
      x = "Offensive Team's # of Pre-Round Wins",
      y = "Defensive Team's # of Pre-Round Wins"
    )
  )
}

val_heatmap_seq_labeller <- function(.df, .label, .num) {
  sprintf(
    '%s\n(%s)', 
    scales::percent(.df[[.label]], accuracy = 1), 
    scales::comma(.df$n)
  )
}

o_series_win_text_layer <- function(
    ..., 
    .df,
    .threshold,
    .labeller, 
    .emphasize
) {
  if(.emphasize == 'low') {
    op <- `<`
    .color <- blackish_background
  } else {
    op <- `>=`
    .color <- 'white'
  }
  list(
    ...,
    heatmap_text_layer(
      .df = .df,
      .op = op,
      .label = 'win_series_prop',
      .num = 'win_series',
      .color = .color,
      .threshold = .threshold,
      .labeller = .labeller,
      .size = 9 / .pt
    )
  )
}

val_heatmap_div_labeller <- function(.df, .label, .num) {
  sprintf(
    '%+.1f\n(%s)', 
    100 * .df[[.label]], 
    scales::comma(.df$n)
  )
}

o_series_win_over_expected_text_layer <- function(
    ..., 
    .df,
    .threshold,
    .labeller, 
    .emphasize
) {
  if(.emphasize == 'low') {
    op <- `<`
    .color <- blackish_background
  } else {
    op <- `>=`
    .color <- 'white'
  }
  list(
    ...,
    heatmap_text_layer(
      .df = .df,
      .op = op,
      .label = 'diff_win_series_prop',
      .num = NULL,
      .color = .color,
      .threshold = .threshold,
      .labeller = .labeller,
      .size = 9 / .pt
    )
  )
}
```

```{r}
#| label: val_rounds-calcs
val_round_and_series_win_prop_by_side <- val_rounds |> 
  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
  summarize(
    n = n(),
    across(c(win_round, win_series), sum)
  ) |> 
  ungroup() |> 
  mutate(
    win_round_prop = win_round / n,
    win_series_prop = win_series / n
  )

val_o_win_prop <- val_round_and_series_win_prop_by_side |> 
  filter(is_offense) |> 
  mutate(
    diff_win_round_prop = win_round_prop - !!val_o_win_prop_const
  ) |> 
  inner_join(
    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
    by = c('pre_cumu_w', 'pre_cumu_l')
  ) |> 
  mutate(
    diff_win_series_prop = win_series_prop - e_win_series_prop
  ) |> 
  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
  drop_25th_round()
```

```{r}
#| label: val_rounds_bothbuy-calcs
val_bothbuy_rounds <- val_rounds |> 
  filter(
    team_buy_type %in% c('semi-buy', 'full-buy'), 
    opponent_buy_type  %in% c('semi-buy', 'full-buy')
  )

val_bothbuy_o_win_prop_const <- val_bothbuy_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)

val_round_and_series_win_prop_by_side_bothbuy <- val_bothbuy_rounds |> 
  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
  summarize(
    n = n(),
    across(c(win_round, win_series), sum)
  ) |> 
  ungroup() |> 
  mutate(
    win_round_prop = win_round / n,
    win_series_prop = win_series / n
  )

val_o_win_prop_bothbuy <- val_round_and_series_win_prop_by_side_bothbuy |> 
  filter(is_offense) |> 
  mutate(
    diff_win_round_prop = win_round_prop - !!val_bothbuy_o_win_prop_const
  ) |> 
  inner_join(
    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
    by = c('pre_cumu_w', 'pre_cumu_l')
  ) |> 
  mutate(
    diff_win_series_prop = win_series_prop - e_win_series_prop
  ) |> 
  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
  drop_25th_round()
```

```{r}
#| label: val-funcs-2
val_pre_swap_rounds <- val_o_win_prop |> 
  mutate(pre_cumu_wl = pre_cumu_w + pre_cumu_l) |> 
  filter(pre_cumu_wl == 12)

val_pre_swap_round_segments <- val_pre_swap_rounds |> 
  transmute(
    pre_cumu_w,
    across(pre_cumu_l, ~.x),
    i = row_number(),
    n = 2
  ) |> 
  uncount(n) |> 
  group_by(i) |> 
  mutate(rn = row_number()) |> 
  ungroup() |> 
  mutate(
    across(pre_cumu_w, ~ifelse(rn == 2, .x + 1, .x))
  ) |> 
  add_row(
    pre_cumu_w = 12,
    pre_cumu_l = 0
  )

val_swap_path <- function(...) {
  list(
    ...,
    geom_path(
      data = val_pre_swap_round_segments,
      color = 'white',
      size = 1.5,
      aes(
        x = pre_cumu_w, 
        y = pre_cumu_l
      )
    )
  )
}
```

```{r}
#| label: p_val_o_round_win_prop
p_val_o_round_win_prop <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_round_prop') +
  val_swap_path() +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_round_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('teal') +
  labs(
    title = 'Offensive Round Win %'
  )
p_val_o_round_win_prop
save_plot_for_slide(p_val_o_round_win_prop)

p_val_o_round_win_prop_bothbuy <- val_o_win_prop_bothbuy |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_round_prop') +
  val_swap_path() +
  heatmap_text_layers(
    .df = val_o_win_prop_bothbuy, 
    .f = o_round_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('teal') +
  labs(
    title = 'Offensive Round Win %'
  )
p_val_o_round_win_prop_bothbuy
save_plot_for_slide(p_val_o_round_win_prop_bothbuy)
```

![](plots/val_o_round_win_prop.png){fig-align="center"}

## What are your chances of winning the series ([COD SnD]{.cod})?

@@

## What are your chances of winning the series ([COD SnD]{.cod})?

@@

## What are your chances of winning the series ([Valorant]{.valorant})?

```{r}
#| label: p_val_o_series_win_prop
p_val_o_series_win_prop <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_series_prop') +
  val_swap_path() +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_series_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('orange') +
  labs(
    title = 'Offensive Series Win %'
  )
p_val_o_series_win_prop
save_plot_for_slide(p_val_o_series_win_prop)
```

![](plots/val_o_series_win_prop.png){fig-align="center"}

## What are your chances of winning the series ([Valorant]{.valorant})?

```{r}
#| label: p_val_o_series_win_prop_over_expected
val_max_diff_win_series_prop <- max(abs(val_o_win_prop$diff_win_series_prop))
p_val_o_series_win_prop_over_expected <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.2,
    .labeller = val_heatmap_div_labeller
  ) +
  val_swap_path() +
  scale_fill_gradient2(
    low = ggsci_brown,
    high = ggsci_cyan,
    mid = 'white',
    limits = c(
      -val_max_diff_win_series_prop,
      +val_max_diff_win_series_prop
    ),
    midpoint = 0
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_val_o_series_win_prop_over_expected
save_plot_for_slide(p_val_o_series_win_prop_over_expected)
```

![](plots/val_o_series_win_prop_over_expected.png){fig-align="center"}

## What are your chances of winning the series ([Valorant]{.valorant})?

```{r}
#| label: p_filt_val_o_series_win_prop_over_expected
filt_val_o_win_prop <- val_o_win_prop |> 
  mutate(
    across(
      diff_win_series_prop,
      ~case_when(
        pre_cumu_w <= 3 & pre_cumu_l <= 3 ~ NA_real_,
        TRUE ~ .x
      )
    )
  )
filt_val_max_diff_win_series_prop <- max(abs(filt_val_o_win_prop$diff_win_series_prop))

p_filt_val_o_series_win_prop_over_expected <- filt_val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = filt_val_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.1,
    .labeller = val_heatmap_div_labeller
  ) +
  val_swap_path() +
  scale_fill_gradient2(
    low = ggsci_brown,
    high = ggsci_cyan,
    mid = 'white',
    limits = c(
      -filt_val_max_diff_win_series_prop,
      +filt_val_max_diff_win_series_prop
    ),
    midpoint = 0
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_filt_val_o_series_win_prop_over_expected
save_plot_for_slide(p_filt_val_o_series_win_prop_over_expected)
```

![](plots/filt_val_o_series_win_prop_over_expected.png){fig-align="center"}

## What are the most common series winning states ([COD SnD]{.cod})?

@@

summarize_streaks <- function(rounds, game = c('cod', 'val')) {
  if (game == 'cod') {
    .max_round <- 11
    .adj <- 0
  } else {
    .max_round <- 25
    .adj <- 1
  }

@@

plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
  if (game == 'cod') {
    .lvls <- sprintf('6-%d', 0:5)
    .axis_x_text_size <- 14
  } else {
    .lvls <- c(sprintf('13-%d', 0:11), '12-12')
    .axis_x_text_size <- 12
  }

@@

cod_streaks_res <- cod_rounds |> summarize_streaks('cod')

p_cod_series_outcome_prop_over_expected <- cod_streaks_res$series |> 
  plot_series_outcome_prop_over_expected('cod') +
  common_cod_labs()
p_cod_series_outcome_prop_over_expected
save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
```

@@

## Should round win percentage in [COD SnD]{.cod} be modeled as constant?

@@

::: fragment
-   In COD, the average number of rounds (**`r avg_actual_cod_rounds_per_series`**) is less than the expected value (**`r avg_expected_cod_rounds_per_series`**)
:::

@@

## What are the most common series winning states ([Valorant]{.valorant})?

```{r}
#| label: p_val_series_outcome_prop_over_expected
val_streaks_res <- val_rounds |> summarize_streaks('val')

p_val_series_outcome_prop_over_expected <- val_streaks_res$series |> 
  plot_series_outcome_prop_over_expected('val') +
  common_val_labs()
p_val_series_outcome_prop_over_expected
save_plot_for_slide(p_val_series_outcome_prop_over_expected)
```

![](plots/val_series_outcome_prop_over_expected.png)

There's a clear bias towards shorter series than expected.

## When do back-to-back round wins occur ([COD SnD]{.cod})?

@@

## Is there evidence for the "hot hand" ([COD SnD]{.cod})?

@@

## Is there evidence for the "hot hand" ([Valorant]{.valorant})?

```{r}
#| label: val_round_win_prop_after_x_wins-save
#| eval: false
val_round_streaks <- val_rounds |> 
  group_by(series_id, team, is_offense) |> 
  mutate(
    won_prior_round1 = lag(win_round, n = 1, default = NA),
    won_prior_round2 = lag(win_round, n = 2, default = NA),
    won_prior_round3 = lag(win_round, n = 3, default = NA),
    won_prior_round4 = lag(win_round, n = 4, default = NA),
    won_prior_round5 = lag(win_round, n = 5, default = NA),
    won_prior_round6 = lag(win_round, n = 6, default = NA),
    won_prior_round7 = lag(win_round, n = 7, default = NA),
    won_prior_round8 = lag(win_round, n = 8, default = NA),
    won_prior_round9 = lag(win_round, n = 9, default = NA)
  ) |> 
  ungroup() |>
  select(
    series_id,
    team,
    is_offense,
    cumu_w,
    round,
    n_rounds,
    win_round,
    starts_with('won_prior_round')
  )

summarize_val_win_prop_after_x_wins_first12r <- function(k) {
  stopifnot((k >= 3) & (k <= 9))
  probs_nx_k <- tibble(
    cumu_w = 4L:11L,
    n_rounds = 12L
  ) |> 
    mutate(
      prior_p = cumu_w / n_rounds,
      expected_poststreak_p = map2_dbl(
        n_rounds, prior_p, 
        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
      )
    )

  cols <- sprintf('won_prior_round%d', 2:k)
  col_syms <- syms(cols)
  val_round_streaks_after_x <- val_round_streaks |> 
    filter(round < 13) |> 
    drop_na(!!!col_syms) |> 
    count(cumu_w, win_round, won_prior_round1, !!!col_syms, sort = TRUE)

  val_round_win_prop_after_x_wins <- val_round_streaks_after_x |> 
    filter(won_prior_round1, !!!col_syms)

  val_round_win_prop_after_x_wins |> 
    group_by(cumu_w) |> 
    mutate(
      total = sum(n),
      prop = n / total
    ) |> 
    ungroup() |> 
    filter(win_round) |> 
    select(cumu_w, n, total, prop) |> 
    arrange(cumu_w) |> 
    inner_join(
      probs_nx_k,
      by = 'cumu_w'
    ) |> 
    nest(data = -c(cumu_w)) |> 
    mutate(
      gt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
          broom::tidy() |>
          pull(p.value) |> 
          round(3)
      ),
      lt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
          broom::tidy() |>
          pull(p.value) |> 
          round(3)
      )
    ) |> 
    unnest(data)
}

summarize_val_win_prop_after_x_wins_second12r <- function(k) {
  stopifnot((k >= 3) & (k <= 9))
  probs_nx_k <- crossing(
    cumu_w = 0L:13L,
    n_rounds = 13L:24L
  ) |> 
    mutate(
      prior_p = cumu_w / n_rounds,
      expected_poststreak_p = map2_dbl(
        n_rounds, prior_p, 
        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
      )
    )

  cols <- sprintf('won_prior_round%d', 2:k)
  col_syms <- syms(cols)
  val_round_streaks_after_x <- val_round_streaks |> 
    filter(round > 12) |> 
    drop_na(!!!col_syms) |> 
    count(n_rounds, cumu_w, win_round, won_prior_round1, !!!col_syms, sort = TRUE)

  val_round_win_prop_after_x_wins <- val_round_streaks_after_x |> 
    filter(won_prior_round1, !!!col_syms)

  val_round_win_prop_after_x_wins |> 
    group_by(n_rounds, cumu_w) |> 
    mutate(
      total = sum(n),
      prop = n / total
    ) |> 
    ungroup() |> 
    filter(win_round) |> 
    select(n_rounds, cumu_w, n, total, prop) |> 
    arrange(n_rounds, cumu_w) |> 
    inner_join(
      probs_nx_k,
      by = c('n_rounds', 'cumu_w')
    ) |> 
    nest(data = -c(n_rounds, cumu_w)) |> 
    mutate(
      gt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
          broom::tidy() |>
          pull(p.value) |> 
          round(3)
      ),
      lt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
          broom::tidy() |>
          pull(p.value) |> 
          round(3)
      )
    ) |> 
    unnest(data)
}

val_round_win_prop_after_x_wins_first12r <- tibble(win_streak = 3L:9L) |> 
  mutate(
    data = map(win_streak, summarize_val_win_prop_after_x_wins_first12r)
  ) |> 
  unnest(data)
save_qs(val_round_win_prop_after_x_wins_first12r)

val_round_win_prop_after_x_wins_second12r <- tibble(win_streak = 3L:9L) |> 
  mutate(
    data = map(win_streak, summarize_val_win_prop_after_x_wins_second12r)
  ) |> 
  unnest(data)
save_qs(val_round_win_prop_after_x_wins_second12r)
```

```{r}
#| label: val_round_win_prop_after_x_wins
#| eval: false
load_qs('val_round_win_prop_after_x_wins_first12r')
load_qs('val_round_win_prop_after_x_wins_second12r')
val_round_win_prop_after_x_wins_first12r |> 
  filter(n > 30) |> 
  mutate(
    gt_signif = gt_p_value <= 0.05
  ) |> 
  ggplot() +
  aes(x = win_streak, y = cumu_w) +
  geom_tile(
    aes(fill = gt_signif)
  ) +
  geom_text(
    aes(label = sprintf(
      '%s | %s\n(%s)',
      scales::percent(prop, accuracy = 1),
      scales::percent(expected_poststreak_p, accuracy = 1),
      scales::comma(total)
    )
    )
  )

val_round_win_prop_after_x_wins_second12r |> 
  filter(n > 30) |> 
  mutate(
    gt_signif = gt_p_value <= 0.05
  ) |> 
  ggplot() +
  aes(x = win_streak, y = cumu_w) +
  geom_tile(
    aes(fill = gt_signif)
  ) +
  geom_text(
    aes(label = sprintf(
      '%s | %s\n(%s)',
      scales::percent(prop, accuracy = 1),
      scales::percent(expected_poststreak_p, accuracy = 1),
      scales::comma(total)
    )
    )
  ) +
  facet_wrap(~n_rounds)

```

```{r}
#| label: cod_round_win_prop_after_xw-eval
#| eval: false
load_qs('val_round_win_prop_after_x_wins_first12r')
val_round_win_prop_after_x_wins_first12r |> 
  transmute(
    `Win Streak` = win_streak,
    `# of Offensive Wins in First 12 Rounds` = cumu_w,
    `N` = scales::comma(total),
    across(c(prop, expected_poststreak_p), ~scales::percent(.x, accuracy = 0.1)),
    across(
      ends_with('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        round(.x, 2) == 1 ~ '1',
        TRUE ~ as.character(round(.x, 2))
      )
    )
  ) |>
  rename(
    `Actual post-streak win %` = prop,
    `Expected post-streak win %` = expected_poststreak_p,
    `Binom. > p-value` = gt_p_value,
    `Binom. < p-value` = lt_p_value
  ) |> 
  knitr::kable()

```

::: fragment
First 12 rounds **only**

TODO
:::

::: fragment
-   There is no evidence for momentum, for both streaks of 2 and 3. In fact, for series that go to 9, 10, or 11 rounds, there is evidence that the streaking teams perform significantly worse than expected in the post-streak round. And for streaks of 4, teams perform worse than expected in series ending in 7, 8, 10, and 11 rounds.
:::

::: fragment
-   Given the nature of how economy is used in the game, perhaps this is not suprising at all.
:::

## Is planting at one site better than the other ([COD SnD]{.cod})?

@@

## Are offensive win %'s different in round 1 ([COD SnD]{.cod})?

@@

plot_round_vs_post_round_slope_chart <- function(df, .round, game = c('cod', 'val')) {
  game <- match.arg(game)
  o_win_rx_prop <- summarize_map_o_round_win_prop(df, .round)
  x1_label <- sprintf('Round %d<br/>offensive win %%', .round)
  x2_label <- sprintf('Post-round %d<br/>offensive win %%', .round)

@@

  is_cod <- game == 'cod'
  if (is_cod) {
    y_lo <- 0.25
    y_hi <- 0.75
  } else {
    y_lo <- 0.45
    y_hi <- 0.55
  }

@@

cod_res_r1 <- cod_rounds |> 
  plot_round_vs_post_round_slope_chart(1, game = 'cod')

@@

## Are offensive win %'s different in round 1 ([Valorant]{.valorant})?

```{r}
#| label: p_val_o_win_r1_vs_post_round_prop
p_val_o_win_r1_vs_post_round_prop <- val_rounds |> 
  plot_round_vs_post_round_slope_chart(1, game = 'val') |> 
  pluck('plot') +
  common_val_labs()
save_plot_for_slide(p_val_o_win_r1_vs_post_round_prop)
```

![](plots/val_o_win_r1_vs_post_round_prop.png){fig-align="center"}

>>>>

cod_rounds <- qs::qread('cod_rounds.qs')
```

@@

font <- 'Titillium Web'
extrafont::loadfonts(quiet = TRUE)
theme_set(theme_minimal())
theme_update(
  text = element_text(family = font),
  title = element_text(size = 14, color = 'white'),
  plot.title = element_text(face = 'bold', size = 20, color = 'white'),
  plot.title.position = 'plot',
  plot.subtitle = element_text(size = 14, color = '#f1f1f1'),
  axis.text = element_text(color = 'white', size = 14),
  axis.title = element_text(size = 14, color = 'white', face = 'bold', hjust = 0.99),
  axis.line = element_blank(),
  panel.grid.major = element_line(color = gray_points),
  panel.grid.minor = element_line(color = gray_points),
  panel.grid.minor.x = element_blank(),
  panel.grid.minor.y = element_blank(),
  strip.text = element_text(color = 'white', size = 16, face = 'bold'),
  plot.margin = margin(10, 10, 10, 10),
  plot.background = element_rect(fill = blackish_background, color = blackish_background),
  plot.caption = element_text(size = 12, color = 'white', hjust = 1),
  plot.caption.position = 'plot',
  plot.tag = ggtext::element_markdown(size = 12, color = 'white', hjust = 0),
  plot.tag.position = c(0.01, 0.01),
  panel.background = element_rect(fill = blackish_background, color = blackish_background)
)
update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
update_geom_defaults('point', list(color = 'white'))
update_geom_defaults('segment', list(color = 'white'))
```

## Search and Destroy (SnD) in Call of Duty (CoD)

::: fragment
-   2020-2022 Call of Duty League (CDL) matches (qualifiers and majors)
-   4v4
-   First to 6 round wins
-   Teams swap sides (offense and defense) after every round
:::

## How does a team win a round of CoD SnD ?

@@

## CoD SnD data overview

@@

## What are your chances of winning the next round?

```{r}
#| label: cod-funcs
common_cod_labs <- function(...) {
  list(
    ...,
    labs(
      caption = 'CDL SnD major and qualifier series, 2020 - 2022'
    )
  )
}

@@

  ggsave(
    plot = p,
    filename = file.path('plots', filename),
    width = width * dpi,
    height = height * dpi,
    units = units,
    dpi = dpi,
    ...
  )
}

@@

## What are your chances of winning the next round?

@@

## What are your chances of winning the series?

@@

## What are your chances of winning the series?

@@

## What are the most common series winning states?

@@

summarize_streaks <- function(rounds) {
  .max_round <- 11
  .adj <- 0

@@

plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
  .lvls <- sprintf('6-%d', 0:5)
  .axis_x_text_size <- 14

@@

cod_streaks_res <- cod_rounds |> summarize_streaks()

p_cod_series_outcome_prop_over_expected <- cod_streaks_res$series |> 
  plot_series_outcome_prop_over_expected() +
  common_cod_labs()
p_cod_series_outcome_prop_over_expected
save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
```

@@

## Should round win percentage be modeled as constant?

@@

::: fragment
-   In CoD, the average number of rounds (**`r avg_actual_cod_rounds_per_series`**) is less than the expected value (**`r avg_expected_cod_rounds_per_series`**)
:::

@@

## When do back-to-back round wins occur?

@@

## Is there evidence for the "hot hand"?

@@

## Is planting at one site better than the other?

@@

## Are offensive win %'s different in round 1?

@@

plot_round_vs_post_round_slope_chart <- function(df, .roun) {
  game <- match.arg(game)
  o_win_rx_prop <- summarize_map_o_round_win_prop(df, .round)
  x1_label <- sprintf('Round %d<br/>offensive win %%', .round)
  x2_label <- sprintf('Post-round %d<br/>offensive win %%', .round)

@@

  y_lo <- 0.25
  y_hi <- 0.75

@@

cod_res_r1 <- cod_rounds |> 
  plot_round_vs_post_round_slope_chart(1)

@@
